---
title: Screen sector statistics to March 2026
author: BFI Research and Statistics Unit
date: last-modified
date-format: long
format: 
  revealjs:
    smaller: true
css: style.css
title-slide-attributes:
  data-background-color: "#e50076"
execute: 
  echo: false
  warning: false
embed-resources: false
---

```{r}
#| label: load-functions
#| file: R/stats.R

```

```{r}
#| label: set-file-path

file_path <- here::here('data/bfi_stats_release_data.xlsx')
```

# UK box office and admissions {background-color="#e50076"}


##

```{r}
#| label: uk-box-office-text

sheet_name <- "uk_box_office"
type <- "boxoffice"
data_and_vars <- load_data(file_path, sheet_name, type)
box_office_data <- uk_box_office(return_type = "data")
```

<div id="left">

In the UK in the period January to `r data_and_vars$latest_month` (`r data_and_vars$latest_period`) `r data_and_vars$latest_year`:

* Box office revenue was £`r scales::comma(round(box_office_data$current))` million, `r ifelse(box_office_data$pct_change_prev >= 0, "up", "down")` `r abs(box_office_data$pct_change_prev)`% on `r data_and_vars$latest_period` `r data_and_vars$latest_year - 1`.

</div>

<div id="right">

```{r}
#| label: uk-box-office
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

uk_box_office()
```

</div>

## 

```{r}
#| label: uk-admissions-text

sheet_name <- 'uk_admissions'
data_and_vars <- load_data(file_path, sheet_name, type)
uk_admissions_data <- uk_admissions(return_type = "data")
```

<div id="left">

* There were `r scales::comma(round(uk_admissions_data$current))` million cinema admissions, `r ifelse(uk_admissions_data$pct_change_prev >= 0, "up", "down")` `r abs(uk_admissions_data$pct_change_prev)`% on `r data_and_vars$latest_period` `r data_and_vars$latest_year - 1`.
* Figures are for all films on release, including event releases and those that started their release prior to the `r data_and_vars$latest_period` period.

</div>

<div id="right">

```{r}
#| label: uk-admissions
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

uk_admissions()
```
</div>

##

```{r}
#| label: uk-admissions-month-text

sheet_name <- 'uk_admissions'
data_and_vars <- load_data(file_path, sheet_name, type)
uk_admissions_month_data <- uk_admissions_month(return_type = "data")
```

<div id="left">

* `r uk_admissions_month_data$max_month` recorded `r data_and_vars$latest_period` `r data_and_vars$latest_year`'s highest monthly admissions, at `r round(uk_admissions_month_data$max_month_admissions, 0)` million.
* *The Housemaid*, *Avatar: Fire & Ash* and *Hamnet* were the highest earning releases of that month.

</div>

<div id="right">

```{r}
#| label: uk-admissions-month
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

uk_admissions_month()
```

</div>

# UK and Republic of Ireland box office {background-color="#783df6"}

##

```{r}
#| label: uk-roi-box-office-text

sheet_name <- 'uk_roi_box_office'
data_and_vars <- load_data(file_path, sheet_name, type)
uk_roi_box_office_data = uk_roi_box_office(return_type = 'data')
```

<div id="left">

At the UK and Republic of Ireland (ROI) box office:

* Revenue for films released in `r data_and_vars$latest_period` `r data_and_vars$latest_year` was £`r round(uk_roi_box_office_data$current, 0)` million, `r ifelse(uk_roi_box_office_data$pct_change_prev >= 0, "up", "down")` `r abs(uk_roi_box_office_data$pct_change_prev)`% on `r data_and_vars$latest_period` `r data_and_vars$latest_year - 1`.
* This excludes event releases.

</div>

<div id="right">

```{r}
#| label: uk-roi-box-office
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

uk_roi_box_office()
```

</div>

##

```{r}
#| label: uk-market-share-percent-text

sheet_name <- 'uk_film_share'
data_and_vars <- load_data(file_path, sheet_name, type)
uk_market_share_percent_data = uk_market_share_percent(return_type = 'data')
```

<div id="left">

* The total market share of all UK qualifying films was `r uk_market_share_percent_data$all_uk_qualifying`%, approximately `r abs(uk_market_share_percent_data$all_pt_change_prev)` percentage `r ifelse(uk_market_share_percent_data$all_pt_change_prev > 1, "points", "point")` `r ifelse(uk_market_share_percent_data$all_pt_change_prev >= 0, "higher", "down")` than `r data_and_vars$latest_period` `r data_and_vars$latest_year - 1`’s UK qualifying share.
<!-- * *Note*: 2025 figures in chart sum to 44% due to rounding. -->

</div>

<div id="right">

```{r}
#| label: uk-market-share-percent
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

uk_market_share_percent()
```

</div>

# Film and HETV production spend {background-color="#1197FF"}

```{r}
#| label: set-variables-spend

sheet_name <- 'uk_production_detail'
type <- 'production'
data_and_vars <- load_data(file_path, sheet_name, type)
metric <- 'UK_spend_m'

all_production_first_data = all_production_first(return_type = 'data')

```

##

<div id="left">

In the UK, in the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year`: 

* The combined total spend on film and high-end television (HETV) production was £`r all_production_first_data$total_first_latest` billion, `r ifelse(all_production_first_data$total_first_pct_change_prev >=0, "up", "down")` `r abs(round(all_production_first_data$total_first_pct_change_prev))`% on the previous 12-month period.
* This graph shows the figures that were 'first reported' for production spend in each 12-month period. 

</div>

<div id="right">

```{r}
#| label: all-production-first
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

all_production_first()
```

</div>

##

```{r}
#| label: all-production-revised-text

all_production_revised_data = all_production_revised(return_type = 'data')
```

<div id="left">

* Production data is revised every period to account for lags in obtaining complete data across all types of productions.
* Combined spend for the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year` was `r ifelse(all_production_revised_data$total_revised_pct_change_prev >=0, "up", "down")` `r abs(round(all_production_revised_data$total_revised_pct_change_prev))`% on revised figures for the previous 12-month period.

</div>

<div id="right">

```{r}
#| label: all-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

all_production_revised()
```

</div>

##

```{r}
#| label: film-hetv-production-revised-text

film_hetv_production_revised_data = film_hetv_production_revised(return_type = 'data')
```

<div id="left">

* HETV accounted for `r film_hetv_production_revised_data$hetv_percent`% of UK production spend in the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year`.

</div>

<div id="right">

```{r}
#| label: film-hetv-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

film_hetv_production_revised()
```

</div>

##

```{r}
#| label: film-production-revised-text

category_select <- 'film'
film_production_data = production_revised(return_type = 'data')
```

<div id="left">

* UK spend on film production was £`r film_production_data$latest` billion for the 12 months ending `r data_and_vars$latest_month` `r data_and_vars$latest_year`, `r ifelse(film_production_data$pct_change_prev >= 0, "up", "down")` `r abs(film_production_data$pct_change_prev)`% compared with revised figures for the 12 months ending `r data_and_vars$latest_month` `r data_and_vars$latest_year - 1`.

</div>

<div id="right">

```{r}
#| label: film-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
production_revised()
```

</div>

##

<div id="left">

The BFI assigns productions to one of three categories:

* Inward investment features (INW)
* Domestic UK features (DOM)
* Co-productions (COP)

See [notes to statistics releases](https://www.bfi.org.uk/industry-data-insights/official-statistics-release-calendar) for full definitions.

</div>

<div id="right">

```{r}
#| label: film-production-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
production_breakdown_revised()
```

</div>

##

<div id="left">

* These graphs plot first reported data against revised data for all productions (ALL) and INW, DOM and COP projects.

</div>

<div id="right">

```{r}
#| label: film-production-facet
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
production_line_facet()
```

</div>

##

```{r}
#| label: hetv-production-revised-text

category_select <- 'hetv'
hetv_production_data = production_revised(return_type = 'data')
```

<div id="left">

* UK spend on HETV projects was £`r hetv_production_data$latest` billion in the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year`, `r ifelse(hetv_production_data$pct_change_prev >= 0, "up", "down")` `r abs(hetv_production_data$pct_change_prev)`% on revised figures for the previous 12-month period.

</div>

<div id="right">

```{r}
#| label: hetv-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

production_revised()
```

</div>

##

<div id="left">

* Spend on co-productions almost doubled compared with revised figures for the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year - 1`.

</div>

<div id="right">

```{r}
#| label: hetv-production-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
production_breakdown_revised()
```

</div>

##

<div id="left">

* *Note:* Individual spend figures for first reported INW and COP projects are not shown for the 12 months to `r data_and_vars$latest_month` 2022 for reasons of disclosure control. 

</div>

<div id="right">

```{r}
#| label: hetv-production-facet
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
production_line_facet()
```

</div>

# Film and HETV production count {background-color="#1197FF"}

```{r}
#| label: set-variables-count

sheet_name <- 'uk_production_detail'
df <- load_data(file_path, sheet_name)
metric <- 'count'
```

##

```{r}
#| label: all-production-count-first-text

all_production_first_data = all_production_first(return_type = 'data')
```

<div id="left">

In the UK, in the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year`:

* Combined production starts were `r ifelse(all_production_first_data$total_first_pct_change_prev >= 0, "up", "down")` `r abs(all_production_first_data$total_first_pct_change_prev)`% on first reported figures for the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year - 1`.

</div>

<div id="right">

```{r}
#| label: all-production-count-first
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

all_production_first()
```

</div>

##

<div id="left">

* Production count for the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year` is lower than for the other periods shown here. However, as previously noted, figures are likely to be revised upward in subsequent statistical releases as more data becomes available.

</div>

<div id="right">

```{r}
#| label: all-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

all_production_revised()
```

</div>

##

```{r}
#| label: film-hetv-production-count-revised-text

film_hetv_production_revised_data = film_hetv_production_revised(return_type = 'data')
```

<div id="left">

* We saw earlier that HETV accounted for the majority of UK production spend in the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year`. In terms of number of productions, however, film accounted for the majority: `r 100 - film_hetv_production_revised_data$hetv_percent`%.

</div>

<div id="right">

```{r}
#| label: film-hetv-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

film_hetv_production_revised()
```

</div>

##

```{r}
#| label: film-production-count-revised-text

category_select <- 'film'
film_production_data = production_revised(return_type = 'data')
```

<div id="left">

* `r film_production_data$latest_unrounded` films were recorded as starting principal photography in the UK in the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year`.

</div>

<div id="right">

```{r}
#| label: film-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
production_revised()
```

</div>

##

<div id="left">

* Lags in obtaining complete data on production activity tend to disproportionately affect counts for domestic UK feature films (DOM), particularly those with budgets of less than £500,000. 

</div>

<div id="right">

```{r}
#| label: film-production-count-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
production_breakdown_revised()
```

</div>

##

<div id="left">

* This lag can be clearly seen in these graphs, which compare first reported project counts to revised project counts across all categories of production.

</div>

<div id="right">

```{r}
#| label: film-production-count-facet
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
production_line_facet()
```

</div>

##

```{r}
#| label: hetv-production-count-revised-text

category_select <- 'hetv'
hetv_production_data = production_revised(return_type = 'data')
```

<div id="left">

* `r hetv_production_data$latest_unrounded` HETV programmes were recorded as starting principal photography in the UK in the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year`.

</div>

<div id="right">

```{r}
#| label: hetv-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
production_revised()
```

</div>

##

<div id="left">

* HETV programme starts in the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year` included 13 feature-length single episode productions.

</div>

<div id="right">

```{r}
#| label: hetv-production-count-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
production_breakdown_revised()
```

</div>

##

<div id="left">

* *Note:* Individual counts for first reported INW and COP projects are not reported for the 12 months to `r data_and_vars$latest_month` 2022 for reasons of disclosure control. 

</div>

<div id="right">

```{r}
#| label: hetv-production-count-facet
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
production_line_facet()
```

</div>

# Certification {background-color="#e94e24"}

```{r}
#| label: load-cert

sheet_name <- 'certification'
type <- 'production'
data_and_vars <- load_data(file_path, sheet_name, type)
```

##

```{r}
#| label: film-cert-final-count-text

category_select <- 'film'
cert_status_select <- 'final'
metric <- 'count'
film_cert_data = certification(return_type = 'data')
```

<div id="left">

In the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year`:

* A total of `r film_cert_data$latest_unrounded` films received final certification, either under the cultural test or as an official co-production.
* Certification is required to access UK tax reliefs and credits for audiovisual and video game expenditure.

</div>

<div id="right">

```{r}
#| label: film-cert-final-count
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

certification()
```

</div>

##

```{r}
#| label: film-cert-final-spend-text

category_select <- 'film'
cert_status_select <- 'final'
metric <- 'uk_spend_m'
film_cert_data = certification(return_type = 'data')
```

<div id="left">

* Films achieving final certification in the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year` had an associated UK production spend of £`r film_cert_data$latest` billion.
* Films and other productions can apply for final certification when they have completed production and are ready to be released.

</div>

<div id="right">

```{r}
#| label: film-cert-final-spend
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

certification()
```

</div>

##

```{r}
#| label: hetv-cert-final-count-text
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
cert_status_select <- 'final'
metric <- 'count'
hetv_cert_data = certification(return_type = 'data')
```

<div id="left">

* `r hetv_cert_data$latest_unrounded` HETV titles received final certification through the cultural test in the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year`.
* There were two co-productions with final certification but details are not included for disclosure control reasons.

</div>

<div id="right">

```{r}
#| label: hetv-cert-final-count
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

certification()
```

</div>

##

```{r}
#| label: hetv-cert-final-spend-text
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
cert_status_select <- 'final'
metric <- 'uk_spend_m'
hetv_cert_data = certification(return_type = 'data')
```

<div id="left">

* HETV productions receiving final certification under the cultural test in the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year` had a UK production spend of £`r hetv_cert_data$latest` billion.

</div>

<div id="right">

```{r}
#| label: hetv-cert-final-spend
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

certification()
```

</div>

##

```{r}
#| label: animation-cert-final-count-text
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'animation_tv'
cert_status_select <- 'final'
metric <- 'count'
anm_cert_data = certification(return_type = 'data')
```

<div id="left">

* `r anm_cert_data$latest_unrounded` animation television programmes received final certification under the cultural test in the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year`.
* There were two co-productions with final certification but details are not included for disclosure control reasons.

</div>

<div id="right">

```{r}
#| label: animation-cert-final-count
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

certification()
```

</div>

##

```{r}
#| label: animation-cert-final-spend-text

category_select <- 'animation_tv'
cert_status_select <- 'final'
metric <- 'uk_spend_m'
anm_cert_data = certification(return_type = 'data')
```

<div id="left">

* Animation TV productions receiving final certification under the cultural test in the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year` had a UK production spend of £`r anm_cert_data$latest_unrounded` million.

</div>

<div id="right">

```{r}
#| label: animation-cert-final-spend
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

certification()
```

</div>

##

```{r}
#| label: childrens-cert-final-count-text

category_select <- 'childrens_tv'
cert_status_select <- 'final'
metric <- 'count'
ctv_cert_data = certification(return_type = 'data')
```

<div id="left">

* `r ctv_cert_data$latest_unrounded` children’s television programmes received final certification under the cultural test in the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year`.
* There was one co-production with final certification but details are not included for disclosure control reasons.

</div>

<div id="right">

```{r}
#| label: childrens-cert-final-count
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

certification()
```

</div>

##

```{r}
#| label: childrens-cert-final-spend-text

category_select <- 'childrens_tv'
cert_status_select <- 'final'
metric <- 'uk_spend_m'
ctv_cert_data = certification(return_type = 'data')
```

<div id="left">

* Children's TV productions receiving final certification under the cultural test in the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year` had a UK production spend of £`r ctv_cert_data$latest_unrounded` million.

</div>

<div id="right">

```{r}
#| label: childrens-cert-final-spend
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

certification()
```

</div>

##

```{r}
#| label: video-games-cert-final-count-text

category_select <- 'video_games'
cert_status_select <- 'final'
metric <- 'count'
vg_cert_data = certification(return_type = 'data')
```

<div id="left">

* `r vg_cert_data$latest_unrounded` video games received final certification in the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year`.
* Video games can only be certified under the cultural test.

</div>

<div id="right">

```{r}
#| label: video-games-cert-final-count
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

certification()
```

</div>

##

```{r}
#| label: video-games-cert-final-spend-text

category_select <- 'video_games'
cert_status_select <- 'final'
metric <- 'uk_spend_m'
vg_cert_data = certification(return_type = 'data')
```

<div id="left">

* Video games receiving final certification in the 12 months to `r data_and_vars$latest_month` `r data_and_vars$latest_year` had a UK production spend of £`r vg_cert_data$latest` billion.

</div>

<div id="right">

```{r}
#| label: video-games-cert-final-spend
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

certification()
```

</div>

# Sources {background-color="#e50076"}

* Box office: Comscore, BFI Research & Statistics Unit
* Admissions: Cinema Advertising Association
* Production: BFI Research & Statistics Unit
* Certification: BFI Research & Statistics Unit, BFI Certification Unit 

See [bfi.org.uk](https://www.bfi.org.uk/industry-data-insights) for more industry data and insights